### 2013-09-28 manuscripts/dpp-msbayes/dpp-msbayes.tex
More work on results of dpp ms.

>>>>

\subsection*{Power analyses: Estimation accuracy}
All of the models we evaluated (Table \ref{tabPriors}) struggled to estimate
the dispersion index of divergence times \divTimeDispersion regardless of which
of the three series of models (Table \ref{tabPowerModels}) the data were
generated under (Figs.\
\labelcref{figPowerAccuracyExpDPP,figPowerAccuracyExpUniform,figPowerAccuracyExpOld,figPowerAccuracyExpUshaped,figPowerAccuracyUniformDPP,figPowerAccuracyUniformUniform,figPowerAccuracyUniformOld,figPowerAccuracyUniformUshaped,figPowerAccuracyOldDPP,figPowerAccuracyOldUniform,figPowerAccuracyOldOld,figPowerAccuracyOldUshaped}).
When the divergence times of the 22 population pairs are randomly drawn from a
series of exponential priors (\powerSeriesExp), the \modelDPP model is the
best estimator of \divTimeDispersion, followed by \modelUshaped (figs.\
\labelcref{figPowerAccuracyExpDPP,figPowerAccuracyExpUniform}
The \modelOld model is strongly biased toward underestimating
\divTimeDispersion, estimating values of zero for most of the replicates across
all the data models of \powerSeriesExp (Figure \ref{figPowerAccuracyExpOld}).
The results of the \modelUshaped model are intermediate between those of
\modelOld and the better performing models \modelDPP and \modelUniform
(Figure \ref{figPowerAccuracyExpUshaped}).

When the true divergence times are randomly drawn from a series of uniform
priors (\powerSeriesUniform), all of the models poorly estimate
\divTimeDispersion (Figs.\
\labelcref{figPowerAccuracyUniformDPP,figPowerAccuracyUniformUniform,figPowerAccuracyUniformOld,figPowerAccuracyUniformUshaped}).
The \modelDPP and \modelUniform models tend to over-estimate the variance in
divergence times (Figs.\
\labelcref{figPowerAccuracyUniformDPP,figPowerAccuracyUniformUniform}), whereas
the \modelOld model, again, underestimates \divTimeDispersion, estimating
values of zero for most replicates across all the data models of
\powerSeriesUniform (Figure \ref{figPowerAccuracyUniformOld}).
Again, the performance of the \modelUshaped model is intermediate between the
\modelOld and \modelDPP/\modelUniform models (Figure
\ref{figPowerAccuracyUniformUshaped}).
This pattern of results across the four models is very similar when applied
to data simulated under the series of models of \powerSeriesOld (Figs.\
\labelcref{figPowerAccuracyOldDPP,figPowerAccuracyOldUniform,figPowerAccuracyOldOld,figPowerAccuracyOldUshaped}).

\subsection*{Power analyses: model-choice}
